Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-10 how.tex
Updates from ShareLaTeX

\section{Related Work}
\subsection{Accessing a Trustworthy model}
The premise of this work is that we do {\em not} have
a ready-to-use

In some domains, there is ready access to 
trustworthy domain model that can offer an assessment
of newly generated examples. For example, in other work
we have used executing source code as the ``model'' to check
if our mutations to test suites
  minimize
test suite size while maximizing the number of statements covered~\cite{}

For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
Also, even when there is an existing model, they can require
constant  maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automatically updated whenever new data arrives.
Further, sometimes  it is easier to access instances of a model's behaviour than the model
itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
Laboratory~\cite{fea02a},  our research partner could not share a
propriety model from within the NASA firewalls. However, they could share 
logs of the input/output of that model.

>>>>

\section{Background and Related Work}
\subsection{Accessing Trustworthy Models}

In some domains, there is ready access to 
trustworthy domain model that can offer an assessment
of newly generated examples. For example, in other work
we have used executing source code as the ``model'' to check
if our mutations to test suites
  minimize
test suite size while maximizing the number of statements covered~\cite{me09m,andrews07,andrews10}.

However, not all domains come with ready-to-use models.
In fact, our experience has been that accessing and/or commissioning
a model can be a labor-intensive process.
For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).

Also, even when there is an existing model, they can require
constant  maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automatically updated whenever new data arrives.

Further, sometimes  it is easier to access instances of a model's behaviour than the model
itself. For example, in prior work with Martin  Feather from the Jet Propulsion
Laboratory~\cite{fea02a},  our research partner could not share a
propriety model from within the NASA firewalls. However, they could share 
logs of the input/output of that model.

In summary, for domains with readily accessible models, we recommend
the kinds of tools that are widely used in the search-based
software engineering community such as NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
deb14,Cui2005a,zhang07:TEC} or our own GALE tool~\cite{krall14}. However,
when those models are not available, we recommend tools like HOW.

\subsection{Planning and AI}
Planning, in the classical AI sense, is a logical procedure
that seeks an ordering on {\em operators} to take some domain
{\em state} from a {\em start} state to a {\em goal} state.
This classical logical approach is known to suffer from
computational bottlenecks~\cite{Bylander1994}. Hence,
like this paper,
many researchers take a probabilistic approach.
That said, the commitment to minimal displacement and the fully-automated
modeling approach of this paper makes it stand apart from, say,
  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.

\subsection{Instance-based Reasoning}
Another  connection to AI is case-based reasoning, or CBR
(a.k.a. reasoning via anology or instance-based reasoning).
CBR seeks to emulate human recollection and adaptation
of past experiences in order to find solutions to current
problems. According to 
Kolodner~\cite{Kolodner1992} and Shank~\cite{Schank1977},
humans do not base their decisions
on complex reductive analysis, but on an instantaneous survey of past experiences.
To put that claim another way, according to CBR theory, 
{\em humans  don’t
think,  they remember.}

CBR is purely based on this direct
adaptation of previous cases based on the similarity of
those cases with the current situation. That is, 
CBR based system have no explicit world model such as the Markov
chains used by, say, Dean et al.~\cite{dean1995planning}).
farming.
Rather, that model is implicit within  the available past
cases in the case cache.

One  advantage of CBR is that
when this  cache is  updated and appended with additional cases, then a CBR system is instantly updated
to the latest findings.
